Tweet Classification: Filtering \\ of Twitter for Company-relevant Tweets

### 2012-12-07 paper/paper.tex
paper

>>>>

\section{Individual Contributions}
Specific team member contributions follow from what we originally stated in our project proposal. Brandon implemented utilities to push and pull tweets from our database in Java. He also researched about and wrote different Pipes that could be used by Mallet to transform the tweets during training. Brandon architected the project structure, and helped edit the project's paper and website. Curtis integrated Mallet into the project, prototyped the testing utilities, and wrote the JsonTweetIterator. He also wrote the majority of the paper, implemented the Twitter-aware tokenizer, and wrote bash scripts to process corpora for testing and analysis. Dan harvested tweets from Twitter and managed a database to store all our content. He designed and implemented the testing utility to compare all combinations of Pipes. Dan performed the statistical analysis and generated the graphs for the paper.

We, Brandon Maxwell, Curtis Ullerich, and Daniel Stiner, hereby concur with the contents of this report, in the knowledge that it is an accurate representation of the work we did and the results we found, for our term project.
